pathway coverage

### 2019-11-27 scripts/06_lefse_res_ggplot.Rmd
update

```{r}
# output the sig unique pathway from the above table for later use in the bar plot
feature  %>% 
  distinct(pathway) %>% 
  write_csv('../data/unique_sig_pathway.csv')
```

>>>>

```{r}
# output the sig unique pathway from the above table for later use in the bar plot
feature  %>% 
  distinct(pathway, .keep_all = T) %>% 
  write_csv('../data/unique_sig_pathway.csv')
```

### 2019-11-27 scripts/24_pathcoverage.Rmd
update

---
title: "pathway coverage"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r}
pwc <- read_tsv('~/melodyP/data/humann2_res/humann2_final_out/humann2_pathcoverage_unstratified.tsv')
```

>>>>

---
title: "pathway coverage"
author: "Anqi Dai"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
library(tidyverse)
library(kableExtra)
```

```{r}
pwc <- read_tsv('~/melodyP/data/humann2_res/humann2_final_out/humann2_pathcoverage_unstratified.tsv') %>% 
  rename(pw = names(.)[1]) %>% 
  rename_all(funs(str_replace(., '_Coverage$',''))) %>% 
  # create a new column just to be pwid 
  mutate(pwid = str_extract(pw, '^.+:')) %>% 
  mutate(pwid = str_replace(pwid, ':',''))

# the pheno info
pheno <- read_csv('../data/cleaned_pheno/final_pheno.csv') %>% 
  select(sampleid = Sampleid, 
         Toxicity,
         CR)
```

```{r}
# get the sig pathways in Melodys project to those two outcomes
sig <- read_csv('../data/unique_sig_pathway.csv') %>% 
  # extract the pw id part
  mutate(pwid = str_extract(pathway, '^.+_PWY|^PWY.+\\d{3,4}'))  %>% 
  mutate(pwid = str_replace_all(pwid, '_', '-'))

# subset the pwc to be the sig ones only
pwc_sig <- pwc %>% 
  filter(pwid %in% sig$pwid) %>% 
  select(-pwid) %>% 
  gather(key = 'sampleid', value = 'cov', names(.)[2]:names(.)[ncol(.)]) %>% 
  left_join(pheno, by  = 'sampleid')

pwc %>% 
  filter(pwid %in% sig$pwid) %>% 
  select(-pwid) %>% 
  kable(caption = 'Look at the table of pathway coverage in each sample') %>% 
  kable_styling()
```

```{r out.width='120%'}
pwc_sig_tox <- pwc_sig %>% 
  group_by(pw, Toxicity) %>% 
  summarise(cov_med = median(cov)) %>% 
  arrange(desc(cov_med)) %>% 
  filter(cov_med > 0)

all_title_fs <- 20
axis_text_fs <- 16

pwc_sig_tox %>% 
  ggplot(aes(x = pw, y = cov_med, fill = Toxicity)) +
  geom_bar( stat = 'identity' , position="dodge") +
  coord_flip() +
  scale_color_manual(values = c('#0099B4', '#AD002A'))  +
  scale_fill_manual(values = c('#0099B4', '#AD002A')) +
  theme_classic() +
  theme(axis.title.y  = element_blank(), 
        axis.title.x = element_text(size=axis_text_fs),
        plot.title = element_text(size=all_title_fs),
        axis.text.x = element_text(size=axis_text_fs),
        legend.position="bottom") +
  labs(title = str_glue('Response to Toxicity') ,
       y = 'Median coverage in each group') + 
  ggsave('../figs/path_coverage_tox.jpg', width = 15, height = 8, dpi = 300)

```

```{r out.width='120%'}

pwc_sig_cr <- pwc_sig %>% 
  group_by(pw, CR) %>% 
  summarise(cov_med = median(cov)) %>% 
  arrange(desc(cov_med)) %>% 
  filter(cov_med > 0)

pwc_sig_cr %>% 
  ggplot(aes(x = pw, y = cov_med, fill = CR)) +
  geom_bar( stat = 'identity' , position="dodge") +
  coord_flip() +
  scale_color_manual(values = c('#ED0000', '#00468B'))  +
  scale_fill_manual(values = c('#ED0000', '#00468B')) +
  theme_classic() +
  theme(axis.title.y  = element_blank(), 
        axis.title.x = element_text(size=axis_text_fs),
        plot.title = element_text(size=all_title_fs),
        axis.text.x = element_text(size=axis_text_fs),
        legend.position="bottom") +
  labs(title = str_glue('Response to CR') ,
       y = 'Median coverage in each group') + 
  ggsave('../figs/path_coverage_CR.jpg', width = 15, height = 8, dpi = 300)
```
